The paper on \Large \bf Blockchain Frontrunning

### 2018-09-17 frontrunning/Latex/sections/paper.tex
[frontrunning] edits till section 3

% !TEX root = ../main.tex
%______________________________________________________________%
\section{Introduction}
\label{sec:intro}

@@

\emph{Front-running} is analogous to any course of action during which a person benefits from prior access to inside or confidential market information about upcoming transactions and trades. This problem can occur in both financial and non-financial systems, however, it is more noticeable within the trading and exchange systems as was originated back in the stock markets. In the old times, all the trades were executed on papers, so in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock. In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders. The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and  \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behavior on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

@@

Further reading on the early details on the history and challenges of detecting and regulating front-running can be found in~\cite{markham1988front} . %add a more recent publication?

Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002}, which then in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in an option, derivative, or other financial instruments overlying a security with some exceptions~\cite{sec2012frontrunning, finra_2012}.

@@

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within any systems. However, blockchains have some inherent characteristic that leave them vulnerable to \emph{front-running} behaviour. Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in Section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
%____________________________________________________________________
%%% The following chunk seem to be redundant and weird. Should we keep it?? 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents on high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps, for the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts. %TODO: this last sentece is a bit weird here! 
%____________________________________________________________________

@@

Due to the novelty characteristics of the underlying technology (blockchains) and the issue of front-running, there are only a few research carried out on this subject in the context of blockchain and decentral ledgers. \\
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in Section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}.  They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} (~\ref{submarineCommits}).

>>>>

% !TEX root = ../main.tex
%______________________________________________________________%
\section{Introduction}

\label{sec:intro}

% @J : intro needs lots of love.

@@

\emph{Front-running} is analogous to any course of action during which a person or entity benefits from prior access to inside or confidential market information about upcoming transactions and trades, albeit the problem can occur in both financial and non-financial systems.  In traditional exchanges, traders would gather in same phsycal locations to announce their position in the market, in case of receiving a large order from a client, the broker might say this loud and other people around the table could be informed. Therefore, a malicious trader would run in front of that order and put his own transaction in-between (before the trade was executed) and hence profit from the price increase of the stock. 
%In fact, a group of market participants obtain non-public market information which allows them to front-run other user\'s trades by putting their orders ahead of those trades and benefit from advance knowledge of pending client orders. 
The two significant factors which cause the front-running practice to happen within the financial markets are (i) imperfect competition and (ii) liquidity uncertainty~\cite{liang2005distressed}. Any sort of front-running activity within the financial markets is considered as an unethical and illegal practice as it is unfairly beneficial for a few market participants who have the privilege of acting on this information and taking advantages at the expense of the investors.

@@

On the years after there were ongoing discussions between self-regulatory exchanges (\eg \textit{CBoE}) and \textit{SEC} to regulate, detect and define laws and policies to deal with front-running~\cite{markham1988front}, with \textit{SEC} stating: 
\begin{quote}
It seems evident that such behaviour on the part of persons with knowledge of imminent transactions which will likely affect the price of the derivative security constitutes an unfair use of such knowledge. \footnote{Securities Exchange Act Release No. 14156, November 19, 1977, (Letter from George A. Fitzsimmons, Secretary, Securities and Exchange Commission to Joseph W. Sullivan, President  CBoE).}
\end{quote}

@@

Further reading on the early details on the history and challenges of detecting and regulating front-running is extensively written by Markham~\cite{markham1988front} . %add a more recent publication?

Initially the front-running policies only applied to certain option markets, later on in 2002, the rule was refined to include the same prohibitions to security futures~\cite{finra_2002},  then again in 2012 with the new amendment, FINRA Rule 5270, the front-running rule was extended to cover trading in options, derivatives, or other financial instruments overlying a security with a few exceptions~\cite{sec2012frontrunning, finra_2012}.

@@

Blockchain technology has received an exceptional amount of attention since it was first introduced as the underlying technology of the cryptocurrency Bitcoin in 2008~\cite{nakamoto2008bitcoin}. Many decentralized applications that are built on top of this technology represent the significance of the blockchain as it completely eliminates the central point of failure within the systems. However, blockchains have some inherent characteristic that leave them vulnerable to information leaks and \emph{front-running} behaviour. Although this data structure is known to be publicly visible to every network participants, information is layered and some of them are easier accessed only by insiders. Any network participants that runs a full node on the blockchain is able to obtain those information and as mentioned in section~\ref{sec:What is front-running?}, this leaves the application vulnerable to front-running. %Decentralized exchanges are a group of blockchain financial applications where front-running can be executed. 
%____________________________________________________________________
%%% The following chunk seem to be redundant and weird. Should we keep it?? 
Bancor \cite{hertzog2017bancor} is an example of such systems in which front-runners benefit from potential price increase of the market stocks (details are provided in~\ref{sec:frontrunningExchanges}). Decentralized namespaces, as blockchain non-financial applications, are another example. Ethereum Name Service and Ghazal \cite{moosavighazal} are such systems in which upon seeing a transaction from Alice to register \texttt{alice.eth}, front-runner can go ahead of her and register this domain name. He can later sell \texttt{alice.eth} to Alice for a higher price and profit.
Another application that is vulnerable to front-running is Initial Coin Offering (ICO) smart contracts. ICO is a method to distribute tokens based on the deposits of the native coin, Ether in the case of Ethereum. After a few hacking incidents of high valued smart contracts~\cite{siegel2016daohack}, ICOs started to implement restrictions and capped how much funds can be gathered. This scarcity of the initial coins made for a competition to incentivize big investors to get in and buy the tokens at a discounted price and sell them to late comers on the open markets~\cite{zetzsche2018ico, li2018initial}. ICOs started to experiment with different fair capping methods, such as reverse dutch auction and dynamic ceilings~\cite{kaal2017initial}.  This competition made ICOs a good opportunity for front-running attacks.  In this paper we use multiple empirical examples to show possibility of front-running on DApps. For the sake of completeness, we use one incident on ICOs, and examples from the Top 25 DApps by recent user counts based on \texttt{DAppRadar.com} ranking. 
%____________________________________________________________________

@@

Due to the novelty characteristics of the underlying technology (blockchain), there are only a few research carried out on the issue of front-running in the context of blockchain and decentral ledgers. \\
Aune~\etal discuss how the lack of time priority between broadcasting a transaction and its validation by miners on a blockchain based system would lead to the market information leakage~\cite{aune2017footprints}. As mentioned in section~\ref{sec:What is front-running?}, the information leakage results the entire system to be vulnerable to the front-running. They also propose a cryptographic approach, similar to commit and reveal(~\ref{CommitmentScheme}), to prevent front-running in decentral systems. %In this approach, which is similar to commit and reveal , a transaction hash (fingerprint) is broadcast to the network to secure time priority while not revealing the information. Once the hash is processed and assigned an index and timestamp, the transaction details are broadcast. This makes the transaction and its hash to be executed at their reserved time priority and not vulnerable to front-running.
Malinova and Park discuss different design settings for financial markets and trading platforms on decentral ledgers~\cite{malinova2017market}. They argue that blockchain brings a new options of transparency which affects traders behaviour, specially in the presence of intermediary front-runners. They model indirect trading costs and use the economic literature on search and trading at decentralized exchanges in their design settings to make front-running costly and inefficient.

Breidenbach~\etal~\cite{breidenbach2018enter} face the front-running issue in the context of automating bug bounties for smart contracts. Upon submitting the bug bounty to the Hydra smart contract, one can front-run the bug report and claim the bounty instead of the original reporter. In order to mitigate this issue they proposed \textit{Submarine Commitments} which we discuss further in section~\ref{submarineCommits}.
